% Awesome-CV style — LaTeX recreation (self-contained, XeLaTeX)
% Inspired by Byungjin Park's Awesome-CV (https://github.com/posquit0/Awesome-CV, MIT)
% Built without the upstream .cls to keep this single-file and tectonic-friendly.

\documentclass[11pt,letterpaper]{article}

\usepackage[
  paperwidth=8.5in, paperheight=11in,
  left=0.55in, right=0.55in, top=0.5in, bottom=0.7in,
  includefoot
]{geometry}

\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{ragged2e}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}
\usepackage{xstring}

% ===== Colors =====
\definecolor{awesomered}{HTML}{CC0000}
\definecolor{awesomesoft}{HTML}{D03F3F}
\definecolor{ink}{HTML}{222222}
\definecolor{muted}{HTML}{666666}

% ===== Fonts =====
% Fall back gracefully if Inter not installed; tectonic ships with default fonts.
\IfFontExistsTF{Inter}{
  \setmainfont{Inter}[
    UprightFont = * Regular,
    BoldFont    = * Bold,
    ItalicFont  = * Italic,
    BoldItalicFont = * Bold Italic,
  ]
}{
  % Latin Modern Sans is a reasonable fallback
  \setmainfont{Latin Modern Sans}
}

\color{ink}

% ===== Section styling: first 3 letters red, rest dark, with underline =====
% Caller passes two args so we don't need string-splitting magic
\newcommand{\awesomesection}[2]{%
  \vspace{0.5em}\par\noindent
  {\fontsize{16pt}{18pt}\bfseries\color{awesomered}#1\color{ink}#2}%
  \par\vspace{-0.5em}%
  {\color{ink}\rule{\linewidth}{0.5pt}}\par
  \vspace{0.3em}%
}

% ===== Entry: org (bold) + location (italic red, right); subtitle (smallcaps) + date (italic red, right) =====
\newcommand{\entry}[4]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    {\fontsize{10.5pt}{12pt}\bfseries #1} & {\fontsize{9.5pt}{11pt}\itshape\color{awesomesoft} #2} \\[0.05em]
    {\fontsize{8.8pt}{10pt}\scshape #3} & {\fontsize{9.5pt}{11pt}\itshape\color{awesomesoft} #4} \\
  \end{tabularx}\par\vspace{0.15em}
}

% Sub-block label (Major Awards, Academic Recognition, etc.)
\newcommand{\sublabel}[1]{\par\vspace{0.3em}{\fontsize{9pt}{11pt}\scshape #1}\par\vspace{0.15em}}

% Honor/award row
\newcommand{\honor}[3]{%
  \begin{tabularx}{\linewidth}{@{}l X r@{}}
    {\fontsize{9pt}{11pt}\itshape\color{awesomesoft} #1} & {\fontsize{9pt}{11pt} #2} & {\fontsize{9pt}{11pt}\itshape\color{awesomesoft} #3}
  \end{tabularx}\par\vspace{0.05em}
}

% Bullet list
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=0.2em,
  parsep=0pt,
  topsep=0.25em,
  before={\fontsize{9pt}{11pt}\selectfont}
}

\renewcommand{\labelitemi}{{\color{muted}\textbf{\textperiodcentered}}}

% ===== Footer =====
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\fontsize{8.5pt}{10pt}\color{muted} Dongwook Kwon \quad{$\cdot$}\quad Curriculum Vitae \quad{$\cdot$}\quad \thepage}

\setlength{\parindent}{0pt}

\begin{document}
\fontsize{9pt}{11.5pt}\selectfont

% ===== HEADER =====
\begin{center}
  {\fontsize{32pt}{36pt}\fontseries{l}\selectfont Dongwook }%
  {\fontsize{32pt}{36pt}\bfseries Kwon}\par
  \vspace{0.15em}
  {\fontsize{9pt}{11pt}\itshape\color{muted} Room 701, Saebit Hall, 20 Gwangun-ro, Nowon-gu, Seoul 01897, Republic of Korea}\par
  \vspace{0.3em}
  {\fontsize{8.8pt}{10.5pt}\selectfont
    +82 10-6612-9246 \enspace{$|$}\enspace
    \href{mailto:tomiyadragon@gmail.com}{tomiyadragon@gmail.com} \enspace{$|$}\enspace
    \href{https://dongwooky.github.io}{dongwooky.github.io} \enspace{$|$}\enspace
    \href{https://github.com/dongwooky}{github/dongwooky} \enspace{$|$}\enspace
    \href{https://linkedin.com/in/dongwooky}{in/dongwooky}
  }
\end{center}

\awesomesection{Exp}{erience}

\entry{Suresoft Technologies}{Seongnam, Gyeonggi, Korea}{AI Engineer, Intelligent Agent Technology Team}{Dec. 2025 -- Present}
\begin{itemize}
  \item Developing an AI validation system utilizing AI agent--based architectures.
  \item Designing and implementing systems to verify and evaluate AI models through autonomous and collaborative AI agents.
  \item Building agentic AI systems to enable systematic, scalable, and reliable AI verification processes.
\end{itemize}

\entry{Bio-Computing and Machine Learning Laboratory, Kwangwoon University}{Seoul, Korea}{Research Assistant}{Aug. 2021 -- Dec. 2025}
\begin{itemize}
  \item Conducted research on deep learning algorithms, focusing on anomaly detection in time-series data, including Electrocardiogram (ECG) and Cyber-Physical Systems (CPS).
  \item Participated in the development of an Active Kill-Switch and Biomarker-Based Defense System for life-threatening IoT medical devices.
\end{itemize}

\entry{LG Electronics Canada}{Toronto, ON, Canada}{Research Project}{Jan. 2025 -- Jul. 2025}
\begin{itemize}
  \item Participating in the development of an assessment framework for agentic AI systems utilizing LLMs to evaluate performance.
\end{itemize}

\entry{Qualcomm Institute, University of California San Diego}{San Diego, CA, USA}{AI Development Project, Summer Program}{Jul. 2022 -- Aug. 2022}
\begin{itemize}
  \item Participated in the Personality-Based Drug Addiction Prediction System project.
  \item Attended seminars on deep learning and machine learning algorithms.
\end{itemize}

\awesomesection{Edu}{cation}

\entry{Kwangwoon University}{Seoul, Korea}{Master of Science in Computer Engineering}{Mar. 2024 -- Feb. 2026}
\begin{itemize}
  \item GPA: 4.33/4.5 (Percentage: 98.1\%)
\end{itemize}

\entry{University of Toronto}{Toronto, ON, Canada}{Graduate Research Program in Mechanical and Industrial Engineering}{Jan. 2025 -- Jul. 2025}
\begin{itemize}
  \item GPA: 3.68/4.0
\end{itemize}

\entry{Kwangwoon University}{Seoul, Korea}{Bachelor of Science in Electronics and Communications Engineering}{Mar. 2019 -- Feb. 2024}
\begin{itemize}
  \item GPA: 3.41/4.5 (Percentage: 88.1\%)
\end{itemize}

\awesomesection{Hon}{ors \& Awards}

\sublabel{Major Awards}
\honor{Aug. 2022}{\textbf{Achievement Award}, Qualcomm Institute AI Development Project --- UC San Diego}{United States}
\honor{Dec. 2021}{\textbf{Gold Award (Ministerial Award)}, 2021 Smart Maritime Logistics Project -- Minister of Oceans and Fisheries}{South Korea}

\sublabel{Academic Recognition}
\honor{Nov. 2025}{\textbf{Outstanding Student Paper Award}, Conference of the Institute of Electronics and Information Engineers}{South Korea}
\honor{Nov. 2024}{\textbf{Best Poster Award (Silver)}, 10th International Biomedical Engineering Conference (IBEC 2024)}{South Korea}
\honor{Nov. 2023}{\textbf{Outstanding Paper Award}, Conference of the Korean Society of Medical and Biological Engineering}{South Korea}

\sublabel{Competitions}
\honor{Dec. 2025}{\textbf{Silver Award}, 23rd Embedded Software Competition (KIISE)}{South Korea}
\honor{Dec. 2022}{\textbf{Bronze Award}, Hanium ICT Mentoring Competition -- FKII}{South Korea}
\honor{Sep. 2022}{\textbf{Excellence Award}, 18th Kwangwoon ICT Exhibition (KWIX) --- Kwangwoon University}{South Korea}
\honor{Oct. 2021}{\textbf{Grand Prize}, MY (Multi-Y) Capstone Design Competition --- Kwangwoon University}{South Korea}

\awesomesection{Pro}{jects}

\entry{Agentic AI Evaluation Framework}{Toronto, ON, Canada}{LG Electronics Canada}{Jan. 2025 -- Present}
\begin{itemize}
  \item Developed an evaluation framework for agentic AI systems using LLMs to assess performance.
\end{itemize}

\entry{AI-based Intrusion Detection and Attack Packet Crafting Technologies for APR1400}{Seoul, Korea}{Sejong University}{Jul. 2022 -- Present}
\begin{itemize}
  \item Developed an AI defense system to protect nuclear power plants from cyber attacks.
\end{itemize}

\entry{Quadruped Robot Using Vision SLAM with a Depth Camera}{Seoul, Korea}{Ministry of Science and ICT}{Apr. 2022 -- Nov. 2022}
\begin{itemize}
  \item Developed an autonomous quadruped robot using a navigation algorithm with SLAM and a depth camera.
\end{itemize}

\entry{Active Kill-Switch and Biomarker-Based Defense for Life-Threatening IoT Medical Devices}{Seoul, Korea}{Kookmin University}{Sep. 2021 -- Dec. 2022}
\begin{itemize}
  \item Developed a security system for heart implant devices using an anomaly detection algorithm.
\end{itemize}

\entry{Development of a Smart Logistics System Using Computer Vision}{Seoul, Korea}{Ministry of Oceans and Fisheries}{Apr. 2021 -- Nov. 2021}
\begin{itemize}
  \item Developed a logistics detection system incorporating location tracking and stack layer identification for containers.
\end{itemize}

\awesomesection{Pub}{lications}

\textbf{Journal Articles}
\begin{itemize}
  \item Y. Nam, J. Lee, H. Lee, \textbf{D. Kwon}, M. Yeo, S. Kim, R. Sohn, and C. Park, ``Designing a remote photoplethysmography-based heart rate estimation algorithm during a treadmill exercise,'' \textit{Electronics}, vol. 14, no. 5, p. 890, 2025.
  \item \textbf{D. Kwon}, Y. Kang, J. Lee, Y. Nam, J. Won, K. K. Kim, D. D. Kim, and C. Park, ``Graph-Enhanced Bidirectional GRU for Anomaly Detection in Power Generation Environments,'' under review at \textit{Data Mining and Knowledge Discovery} (Springer Nature), 2025.
\end{itemize}

\textbf{Conference Papers}
\begin{itemize}
  \item R. Chang\textsuperscript{$\dagger$}, \textbf{D. Kwon}\textsuperscript{$\dagger$}, J. Lee\textsuperscript{$\dagger$}, and N. Verma, ``CascadeDebate: Multi-Agent Deliberation for Cost-Aware LLM Cascades,'' in \textit{Proc. 64th Annu. Meeting Assoc. Comput. Linguistics (ACL) -- Industry Track (Poster)}, 2026. \textsuperscript{$\dagger$}Equal contribution
  \item J. Lee\textsuperscript{$\dagger$}, R. Chang\textsuperscript{$\dagger$}, \textbf{D. Kwon}\textsuperscript{$\dagger$}, H. Singh, and N. Verma, ``GEMMAS: Graph-based Evaluation Metrics for Multi Agent Systems,'' in \textit{Proceedings of the EMNLP 2025 Industry Track (Oral)}, 2025. \textsuperscript{$\dagger$}Equal contribution
  \item \textbf{D. Kwon}, M. Kim, Y. Kang, J. Lee, and C. Park, ``Hybrid neural network model for anomaly detection in implantable devices using graph attention networks and transformers,'' in \textit{Proc. 10th Int. Biomed. Eng. Conf. (IBEC)}, 2024. --- \textbf{Best Poster Award -- Silver Winner}
  \item \textbf{D. Kwon}, Y. Kang, and C. Park, ``Enhancing medical device security with GNN-GRU anomaly detection model,'' in \textit{Proc. 62nd KOSOMBE Autumn Conf.}, pp.~204--205, 2023. --- \textbf{Outstanding Paper Award}
\end{itemize}

\awesomesection{Pat}{ents}

\begin{itemize}
  \item \textbf{Issued Patent}, ``Method for Implantable Medical Device to Detect Anomaly in Real Time,'' Patent No. KR 10-2961984, Issued on April 30, 2026.
  \item \textbf{Issued Patent}, ``GPT API-Based Network Anomaly Detection,'' Patent No. KR 10-2848814, Issued on August 18, 2025.
\end{itemize}

\awesomesection{Lea}{dership Experience}

\begin{itemize}
  \item \textbf{President}, Kwangwoon International Student Association --- Lead intercultural programs and student engagement initiatives.
  \item \textbf{Director of Filming and Editing}, Kwangwoon Broadcasting Center (KWBC) --- Oversaw media production and content delivery.
  \item \textbf{Class Representative}, Dept. of Electronics and Communications Engineering --- Represented student interests in academic affairs.
  \item \textbf{Executive Member}, Amateur Radio Club --- Organized radio workshops and technical exhibitions.
\end{itemize}

\end{document}
