% Upstream ModernCV by Xavier Danaux (CTAN)
% Source: https://ctan.org/pkg/moderncv (LPPL)
% Class shipped with TeX Live — no local .cls copy needed.
% GENERATED FROM data/cv.yaml — edit yaml + run scripts/sync.py, not this file.

\documentclass[11pt,letterpaper,sans]{moderncv}

% Styles: classic, casual, banking, oldstyle, fancy
\moderncvstyle{banking}
% Colors: blue, orange, green, red, purple, grey, black
\moderncvcolor{blue}

\usepackage[scale=0.82,top=1.0in,bottom=1.0in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*,itemsep=0.2em,topsep=0.1em}

% Widen the date column (left margin) to fit longer date ranges
\setlength{\hintscolumnwidth}{1.6in}
\AtBeginDocument{\recomputelengths}

% --- Personal data ---
\name{Dongwook}{Kwon}
\title{AI Engineer \textbullet\ Agentic AI Systems}
\address{11F, 37, Geumto-ro 80beon-gil, Sujeong-gu, Seongnam-si}{Gyeonggi-do, 13453, South Korea}{}
\phone[mobile]{+82~10-6612-9246}
\email{dwkwon@suresofttech.com}
\homepage{dongwooky.github.io}
\social[github]{dongwooky}
\social[linkedin]{dongwooky}

\begin{document}
\makecvtitle

%---------------- EXPERIENCE ----------------
\section{Experience}

\cventry{Dec.\ 2025 -- Present}{AI Engineer, Intelligent Agent Technology Team}{Suresoft Technologies}{Seongnam-si, Korea}{}{%
  \begin{itemize}
    \item Developing an AI validation system utilizing AI agent--based architectures for enterprise model verification.
    \item Designing autonomous and collaborative AI agents that verify and evaluate machine-learning models at scale.
    \item Engineered and delivered a critical agent-based codebase for a mission-critical vehicle control data project for Hyundai Motor Company.
  \end{itemize}}

\cventry{Aug.\ 2021 -- Dec.\ 2025}{Research Assistant}{Bio-Computing and Machine Learning Laboratory, Kwangwoon University}{Seoul, Korea}{}{%
  \begin{itemize}
    \item Researched deep-learning algorithms for anomaly detection in complex time-series data, focusing on critical cyber-physical systems including nuclear power generation environments.
    \item Co-developed an Active Kill-Switch and Biomarker-Based Defense System for life-threatening IoT medical devices.
    \item Published in EMNLP 2025 (Oral) and ACL 2026; co-author on two granted Republic of Korea patents.
  \end{itemize}}

\cventry{Jan.\ 2025 -- Jul.\ 2025}{Visiting Researcher}{LG Electronics Canada (with University of Toronto)}{Toronto, ON, Canada}{}{%
  \begin{itemize}
    \item Built an LLM-driven assessment framework for evaluating performance of agentic AI systems.
    \item Work fed directly into peer-reviewed publications at EMNLP 2025 and ACL 2026.
  \end{itemize}}

\cventry{Jul.\ 2022 -- Aug.\ 2022}{AI Development Project Participant, Summer Program}{Qualcomm Institute, University of California San Diego}{San Diego, CA, USA}{}{%
  \begin{itemize}
    \item Built a personality-based drug-addiction prediction system using machine-learning models.
    \item Recognized with the program's Achievement Award.
  \end{itemize}}

%---------------- EDUCATION ----------------
\section{Education}

\cventry{Mar.\ 2024 -- Feb.\ 2026}{M.S.\ in Computer Engineering}{Kwangwoon University}{Seoul, Korea}{\textit{GPA: 4.33/4.5 (98.1\%)}}{}

\cventry{Jan.\ 2025 -- Jul.\ 2025}{Graduate Research Program}{University of Toronto}{Toronto, ON, Canada}{\textit{GPA: 3.68/4.0}}{}

\cventry{Mar.\ 2019 -- Feb.\ 2024}{B.S.\ in Electronics and Communications Engineering}{Kwangwoon University}{Seoul, Korea}{\textit{GPA: 3.41/4.5 (88.1\%)}}{}

%---------------- HONORS & AWARDS ----------------
\section{Honors \& Awards}

\subsection{Major Awards}
\cvitem{Aug.\ 2022}{\textbf{Achievement Award}, Qualcomm Institute AI Development Project --- UC San Diego \hfill \textit{United States}}
\cvitem{Dec.\ 2021}{\textbf{Gold Award (Ministerial Award)}, 2021 Smart Maritime Logistics Project --- Minister of Oceans and Fisheries \hfill \textit{South Korea}}

\subsection{Academic Recognition}
\cvitem{Nov.\ 2025}{\textbf{Outstanding Student Paper Award}, Conference of the Institute of Electronics and Information Engineers \hfill \textit{South Korea}}
\cvitem{Nov.\ 2024}{\textbf{Best Poster Award (Silver)}, 10th International Biomedical Engineering Conference (IBEC 2024) \hfill \textit{South Korea}}
\cvitem{Nov.\ 2023}{\textbf{Outstanding Paper Award}, Conference of the Korean Society of Medical and Biological Engineering \hfill \textit{South Korea}}

\subsection{Competitions}
\cvitem{Dec.\ 2025}{\textbf{Silver Award}, 23rd Embedded Software Competition (KIISE) \hfill \textit{South Korea}}
\cvitem{Dec.\ 2022}{\textbf{Bronze Award}, Hanium ICT Mentoring Competition --- FKII \hfill \textit{South Korea}}
\cvitem{Sep.\ 2022}{\textbf{Excellence Award}, 18th Kwangwoon ICT Exhibition (KWIX) --- Kwangwoon University \hfill \textit{South Korea}}
\cvitem{Oct.\ 2021}{\textbf{Grand Prize}, MY (Multi-Y) Capstone Design Competition --- Kwangwoon University \hfill \textit{South Korea}}

%---------------- PROJECTS ----------------
\section{Funded Research Projects}

\cventry{Jan.\ 2025 -- Present}{Agentic AI Evaluation Framework}{LG Electronics Canada}{Toronto, ON, Canada}{}{Developed an evaluation framework for agentic AI systems using LLMs to assess performance.}

\cventry{Jul.\ 2022 -- Present}{AI Intrusion Detection for APR1400}{Sejong University}{Seoul, Korea}{}{Developed an AI defense system to protect nuclear power plants from cyber attacks.}

\cventry{Apr.\ 2022 -- Nov.\ 2022}{Quadruped Robot with Vision SLAM}{Ministry of Science and ICT}{Seoul, Korea}{}{Developed an autonomous quadruped robot using a navigation algorithm with SLAM and a depth camera.}

\cventry{Jul.\ 2022 -- Aug.\ 2022}{Personality-Based Drug Addiction Prediction System}{Qualcomm Institute, University of California San Diego}{San Diego, CA, USA}{}{Developed a personality-based drug addiction prediction system using a machine learning model.}

\cventry{Sep.\ 2021 -- Dec.\ 2022}{Active Kill-Switch and Biomarker-Based Defense for IoT Medical Devices}{Kookmin University}{Seoul, Korea}{}{Developed a security system for heart implant devices using an anomaly detection algorithm.}

%---------------- PUBLICATIONS ----------------
\section{Publications}

\subsection{Journal Articles}
\cvitem{2025}{Y.~Nam, J.~Lee, H.~Lee, \textbf{D.~Kwon}, M.~Yeo, S.~Kim, R.~Sohn, and C.~Park, ``Designing a remote photoplethysmography-based heart rate estimation algorithm during a treadmill exercise,'' \emph{Electronics}, vol.~14, no.~5, p.~890, 2025.}
\cvitem{2025}{\textbf{D.~Kwon}, Y.~Kang, J.~Lee, Y.~Nam, J.~Won, K.~K.~Kim, D.~D.~Kim, and C.~Park, ``Graph-Enhanced Bidirectional GRU for Anomaly Detection in Power Generation Environments,'' under review at \emph{Data Mining and Knowledge Discovery (Springer Nature)}, 2025.}

\subsection{Conference Papers}
\cvitem{2026}{R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, J.~Lee$^{\dagger}$, and N.~Verma, ``CascadeDebate: Multi-Agent Deliberation for Cost-Aware LLM Cascades,'' in \emph{Proc.~64th Annu.\ Meeting Assoc.\ Comput.\ Linguistics (ACL) --- Industry Track (Poster)}, 2026.\ \ $^{\dagger}$Equal contribution.}
\cvitem{2025}{J.~Lee$^{\dagger}$, R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, H.~Singh, and N.~Verma, ``GEMMAS: Graph-based Evaluation Metrics for Multi Agent Systems,'' in \emph{Proceedings of the EMNLP 2025 Industry Track (Oral)}, 2025.\ \ $^{\dagger}$Equal contribution.}
\cvitem{2024}{\textbf{D.~Kwon}, M.~Kim, Y.~Kang, J.~Lee, and C.~Park, ``Hybrid neural network model for anomaly detection in implantable devices using graph attention networks and transformers,'' in \emph{Proc.\ 10th Int.\ Biomed.\ Eng.\ Conf.\ (IBEC)}, 2024.\ \textbf{Best Poster Award --- Silver.}}
\cvitem{2023}{\textbf{D.~Kwon}, Y.~Kang, and C.~Park, ``Enhancing medical device security with GNN-GRU anomaly detection model,'' in \emph{Proc.\ 62nd KOSOMBE Autumn Conf.}, pp.~204--205, 2023.\ \textbf{Outstanding Paper Award.}}

%---------------- PATENTS ----------------
\section{Patents}
\cvitem{Apr 2026}{\textbf{Issued Patent}, ``Method for Implantable Medical Device to Detect Anomaly in Real Time,'' KR 10-2961984.}
\cvitem{Aug 2025}{\textbf{Issued Patent}, ``GPT API-Based Network Anomaly Detection,'' KR 10-2848814.}
\cvitem{Aug 2024}{\textbf{Patent Application}, ``Categorical Data of Networks Based Network Anomaly Detection Apparatus and Method Thereof,'' KR 10-2024-0110559.}

%---------------- LEADERSHIP ----------------
\section{Leadership Experience}
\cvitem{}{\textbf{President}, Kwangwoon International Student Association --- Lead intercultural programs and student engagement initiatives.}
\cvitem{}{\textbf{Director of Filming and Editing}, Kwangwoon Broadcasting Center (KWBC) --- Oversaw media production and content delivery.}
\cvitem{}{\textbf{Class Representative}, Dept. of Electronics and Communications Engineering --- Represented student interests in academic affairs.}
\cvitem{}{\textbf{Executive Member}, Amateur Radio Club --- Organized radio workshops and technical exhibitions.}

\end{document}
