%!TEX TS-program = xelatex
% Upstream Deedy Resume (OpenFonts variant) by Debarghya Das
% Source: https://github.com/deedy/Deedy-Resume (Apache 2.0)
% Trimmed to fit Deedy's one-page constraint.
% GENERATED FROM data/cv.yaml — edit yaml + run scripts/sync.py, not this file.

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

\begin{document}

\lastupdated

\namesection{Dongwook}{Kwon}{
  \urlstyle{same}\href{https://dongwooky.github.io}{dongwooky.github.io} $|$ \href{mailto:dwkwon@suresofttech.com}{dwkwon@suresofttech.com} \\
  +82 10-6612-9246 $|$ \href{https://github.com/dongwooky}{github.com/dongwooky} $|$ \href{https://linkedin.com/in/dongwooky}{in/dongwooky}
}

\begin{minipage}[t]{0.33\textwidth}

\section{Education}
\subsection{Kwangwoon Univ.}
\descript{M.S.\ Computer Engineering}
\location{Feb 2026 $|$ Seoul, Korea}
GPA 4.33 / 4.5 (98.1\%)\sectionsep

\subsection{Univ. of Toronto}
\descript{Grad Research, Mech \& Ind. Eng.}
\location{Jul 2025 $|$ Toronto}
GPA 3.68 / 4.0\sectionsep

\subsection{Kwangwoon Univ.}
\descript{B.S.\ Electronics \& Comms}
\location{Feb 2024 $|$ Seoul, Korea}
GPA 3.41 / 4.5 (88.1\%)\sectionsep

\section{Links}
Github://~ \href{https://github.com/dongwooky}{\bf dongwooky} \\
LinkedIn://~ \href{https://linkedin.com/in/dongwooky}{\bf dongwooky}
\sectionsep

\section{Skills}
\subsection{Daily}
Python \textbullet{} PyTorch \textbullet{} Transformers \textbullet{} LangChain \textbullet{} Docker \textbullet{} CUDA
\sectionsep

\subsection{Familiar}
C/C++ \textbullet{} MATLAB \textbullet{} TensorFlow \textbullet{} scikit-learn
\sectionsep

\subsection{Domains}
Agentic AI \textbullet{} Multi-Agent LLM \textbullet{} GNN \textbullet{} Anomaly Detection
\sectionsep

\section{Awards}
2025 \textbar{} \textbf{Silver}, KIISE Embedded SW \\
2025 \textbar{} \textbf{Outstanding}, IEIE Conf. \\
2024 \textbar{} \textbf{Best}, IBEC Best Poster \\
2023 \textbar{} \textbf{Outstanding}, KOSOMBE \\
2022 \textbar{} \textbf{Achievement}, UCSD QC Inst. \\
2021 \textbar{} \textbf{Gold Gold}, Maritime Logistics

\sectionsep

\section{Patents}
KR 10-2961984 \\
\textit{Real-time anomaly detection for implantable medical devices} \\[0.3em]
KR 10-2848814 \\
\textit{GPT API-Based Network Anomaly Detection}
\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

\section{Experience}

\runsubsection{Suresoft Technologies}
\descript{$|$ AI Engineer, Intelligent Agent Team}
\location{Dec 2025 -- Present $|$ Seongnam, Korea}
\vspace{0.4em}
\begin{tightemize}
\item Developing AI validation system using agentic AI architectures for enterprise model verification.
\item Designing autonomous and collaborative agents for systematic AI verification.
\end{tightemize}
\sectionsep

\runsubsection{Bio-Computing \& ML Lab, Kwangwoon University}
\descript{$|$ Research Assistant}
\location{Aug 2021 -- Dec 2025 $|$ Seoul, Korea}
\vspace{0.4em}
\begin{tightemize}
\item Deep-learning anomaly detection in time-series (ECG, cyber-physical systems).
\item EMNLP 2025 (Oral), ACL 2026; two granted KR patents.
\end{tightemize}
\sectionsep

\runsubsection{LG Electronics Canada}
\descript{$|$ Visiting Researcher}
\location{Jan 2025 -- Jul 2025 $|$ Toronto, ON, Canada}
\vspace{0.4em}
\begin{tightemize}
\item Built LLM-driven assessment framework for evaluating agentic AI systems.
\end{tightemize}
\sectionsep

\runsubsection{Qualcomm Institute, UC San Diego}
\descript{$|$ AI Development (Summer)}
\location{Jul 2022 -- Aug 2022 $|$ San Diego, CA, USA}
\vspace{0.4em}
\begin{tightemize}
\item Personality-based drug-addiction prediction. Achievement Award.
\end{tightemize}
\sectionsep

\section{Research \& Projects}

\runsubsection{Agentic AI Evaluation Framework} \descript{$|$ LG Canada}
\location{2025 -- Present}
LLM-based evaluation framework for agentic AI systems.
\sectionsep

\runsubsection{AI Intrusion Detection for APR1400} \descript{$|$ Sejong U.}
\location{2022 -- Present}
AI defense for nuclear plant control networks.
\sectionsep

\runsubsection{Quadruped Robot with Vision SLAM} \descript{$|$ MSIT}
\location{Apr -- Nov 2022}
Autonomous SLAM + depth-camera navigation.
\sectionsep

\section{Publications}
R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, J.~Lee$^{\dagger}$, and N.~Verma\ ``CascadeDebate: Multi-Agent Deliberation for Cost-Aware LLM Cascades,'' \emph{ACL 2026 --- Industry (Poster)}.\\[0.15em]

J.~Lee$^{\dagger}$, R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, H.~Singh, and N.~Verma\ ``GEMMAS: Graph-based Evaluation Metrics for Multi Agent Systems,'' \emph{EMNLP 2025 --- Industry (Oral)}.\\[0.15em]

\textbf{D.~Kwon}, M.~Kim, Y.~Kang, J.~Lee, and C.~Park\ ``Hybrid GAT + Transformer for implantable-device anomaly detection,'' \emph{IBEC 2024} --- Best Poster Silver.\\[0.15em]

\textbf{D.~Kwon}, Y.~Kang, and C.~Park\ ``Enhancing medical device security with GNN-GRU anomaly detection model,'' \emph{KOSOMBE 2023} --- Outstanding Paper Award.
\end{minipage}
\end{document}
