% Upstream Twenty Seconds Curriculum Vitae by Carmine Spagnuolo
% Source: https://github.com/spagnuolocarmine/TwentySecondsCurriculumVitae-LaTex (MIT)
% Class copied locally. No profile photo set (would normally go in left sidebar).

\documentclass[]{twentysecondcv}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%
%% PROFILE SIDE BAR %%
%%%%%%%%%%%%%%%%%%%%%%

% \profilepic{...}    % omit photo (placeholder slot left blank)
\cvname{Dongwook Kwon}
\cvjobtitle{AI Engineer}
\cvaddress{Seoul, Republic of Korea}
\cvnumberphone{+82 10-6612-9246}
\cvmail{tomiyadragon@gmail.com}
\cvsite{dongwooky.github.io}

\aboutme{%
AI engineer focused on agentic AI systems and LLM-based multi-agent
evaluation. Research background in deep-learning anomaly detection for
time-series data (ECG, cyber-physical systems). Published at EMNLP 2025
(Oral) and ACL 2026; co-author on two granted Republic of Korea patents.
}

% Skills bar (label / level 0--6)
\skills{%
  {Python/6},
  {PyTorch \& Transformers/5.5},
  {C/C++/4.5},
  {LangChain \& LLMs/5},
  {Linux \& Docker/5},
  {CUDA/4},
  {MATLAB/4}
}

% Skills text (compact below the bar)
\skillstext{{Agentic AI/5.5},{Multi-Agent LLM/5},{GNN/4.5},{Anomaly Detection/5}}

\makeprofile

%%%%%%%%%%%%%%%%%%
%%%%%% BODY %%%%%%
%%%%%%%%%%%%%%%%%%

\section{about}
AI Engineer at Suresoft Technologies' Intelligent Agent Technology Team.
Master's in Computer Engineering at Kwangwoon University. Visiting research
at LG Electronics Canada with the University of Toronto.

\section{education}
\begin{twenty}
  \twentyitem
    {2024--2026}
    {M.S.\ {\normalfont in Computer Engineering}}
    {Kwangwoon University, Seoul}
    {GPA 4.33 / 4.5 (98.1\%). Bio-Computing \& Machine Learning Laboratory.}
  \twentyitem
    {2025}
    {Graduate Research Program}
    {University of Toronto, Canada}
    {Mechanical and Industrial Engineering. GPA 3.68 / 4.0.}
  \twentyitem
    {2019--2024}
    {B.S.\ {\normalfont in Electronics and Communications Engineering}}
    {Kwangwoon University, Seoul}
    {GPA 3.41 / 4.5 (88.1\%).}
\end{twenty}

\section{experience}
\begin{twenty}
  \twentyitem
    {2025--Now}
    {AI Engineer, Intelligent Agent Technology Team}
    {Suresoft Technologies, Seongnam}
    {Developing an AI validation system using agentic AI architectures for enterprise model verification. Designing autonomous and collaborative agents that verify and evaluate ML models at scale.}
  \twentyitem
    {2021--2025}
    {Research Assistant}
    {Bio-Computing \& ML Lab, Kwangwoon U.}
    {Deep-learning anomaly detection in time-series (ECG, cyber-physical systems). Co-developed an Active Kill-Switch and Biomarker-Based Defense System for IoT medical devices.}
  \twentyitem
    {2025}
    {Visiting Researcher}
    {LG Electronics Canada (with U.\ of Toronto)}
    {Built an LLM-driven assessment framework for evaluating performance of agentic AI systems.}
  \twentyitem
    {2022}
    {AI Development Project, Summer Program}
    {Qualcomm Institute, UC San Diego}
    {Personality-based drug-addiction prediction system. Recognized with the program's Achievement Award.}
\end{twenty}

\section{publications}
\begin{twentyshort}
  \twentyitemshort
    {2026}
    {\textbf{D. Kwon}$^{\dagger}$ et al.\ ``CascadeDebate: Multi-Agent Deliberation for Cost-Aware LLM Cascades.'' \emph{ACL 2026 --- Industry (Poster)}.}
  \twentyitemshort
    {2025}
    {\textbf{D. Kwon}$^{\dagger}$ et al.\ ``GEMMAS: Graph-based Evaluation Metrics for Multi-Agent Systems.'' \emph{EMNLP 2025 --- Industry (Oral)}.}
  \twentyitemshort
    {2025}
    {\textbf{D. Kwon} et al.\ ``Graph-Enhanced Bi-GRU for Anomaly Detection in Power Generation Environments.'' \emph{DMKD} (Springer Nature, under review).}
  \twentyitemshort
    {2024}
    {\textbf{D. Kwon} et al.\ ``Hybrid GAT + Transformer for implantable-device anomaly detection.'' \emph{IBEC 2024} --- Best Poster Silver.}
\end{twentyshort}

\section{awards}
\begin{twentyshort}
  \twentyitemshort
    {2025}
    {\textbf{Silver Award}, 23rd Embedded Software Competition (KIISE).}
  \twentyitemshort
    {2025}
    {\textbf{Outstanding Student Paper}, IEIE Conference.}
  \twentyitemshort
    {2024}
    {\textbf{Best Poster Silver}, IBEC 2024.}
  \twentyitemshort
    {2022}
    {\textbf{Achievement Award}, Qualcomm Institute AI Project --- UC San Diego.}
  \twentyitemshort
    {2021}
    {\textbf{Gold (Ministerial)}, Smart Maritime Logistics Project --- Minister of Oceans and Fisheries.}
\end{twentyshort}

\section{patents}
\begin{twentyshort}
  \twentyitemshort
    {Apr 2026}
    {KR 10-2961984 --- Real-time anomaly detection for implantable medical devices.}
  \twentyitemshort
    {Aug 2025}
    {KR 10-2848814 --- GPT API-Based Network Anomaly Detection.}
\end{twentyshort}

\end{document}
