% Upstream EuropeCV (Europass format) by Nicola Vitacolonna / Giuseppe Silano
% Source: https://ctan.org/pkg/europecv (LPPL)
% Class shipped with TeX Live — no local .cls copy needed.

\documentclass[helvetica,narrow]{europecv}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{hyperref}
\usepackage[a4paper,left=2cm,right=2cm,top=2cm,bottom=3cm]{geometry}

% --- Personal data ---
\ecvname{Kwon, Dongwook}
\ecvfootername{Dongwook Kwon}
\ecvaddress{Room 701, Saebit Hall, 20 Gwangun-ro, Nowon-gu, Seoul 01897, Republic of Korea}
\ecvtelephone{+82~10-6612-9246}
\ecvemail{\href{mailto:tomiyadragon@gmail.com}{tomiyadragon@gmail.com}}
\ecvhomepage{\url{https://dongwooky.github.io}}
\ecvnationality{Republic of Korea}
\ecvdateofbirth{}
\ecvgender{Male}
\ecvdate{\today}

\begin{document}
\selectlanguage{english}
\begin{europecv}

\ecvpersonalinfo

%==============================================================
\section{Work experience}

\ecvitem{Dec.~2025 -- Present}{\textbf{AI Engineer}, Intelligent Agent Technology Team\newline
  Suresoft Technologies, Seongnam, Republic of Korea\newline
  \emph{Main activities:} Developing an AI validation system using AI agent--based
  architectures. Designing autonomous and collaborative AI agents that verify and
  evaluate machine-learning models at scale. Building agentic AI systems for
  systematic, scalable, and reliable AI verification.}

\ecvitem{Aug.~2021 -- Dec.~2025}{\textbf{Research Assistant}\newline
  Bio-Computing and Machine Learning Laboratory, Kwangwoon University, Seoul\newline
  \emph{Main activities:} Researched deep-learning algorithms for anomaly detection
  in time-series data (ECG, cyber-physical systems). Co-developed an Active
  Kill-Switch and Biomarker-Based Defense System for life-threatening IoT medical
  devices. Two granted Republic of Korea patents.}

\ecvitem{Jan.~2025 -- Jul.~2025}{\textbf{Visiting Researcher}\newline
  LG Electronics Canada (with University of Toronto), Toronto, ON, Canada\newline
  \emph{Main activities:} Built an LLM-driven assessment framework for evaluating
  performance of agentic AI systems. Work fed into EMNLP 2025 and ACL 2026
  publications.}

\ecvitem{Jul.~2022 -- Aug.~2022}{\textbf{AI Development Project Participant}, Summer Program\newline
  Qualcomm Institute, University of California San Diego, San Diego, CA, USA\newline
  \emph{Main activities:} Personality-based drug-addiction prediction system using
  machine-learning models. Recognized with the program's Achievement Award.}

%==============================================================
\section{Education and training}

\ecvitem{Mar.~2024 -- Feb.~2026}{\textbf{Master of Science in Computer Engineering}\newline
  Kwangwoon University, Seoul, Republic of Korea\newline
  GPA: 4.33 / 4.5 (98.1\%).}

\ecvitem{Jan.~2025 -- Jul.~2025}{\textbf{Graduate Research Program in Mechanical and Industrial Engineering}\newline
  University of Toronto, Canada \newline
  GPA: 3.68 / 4.0.}

\ecvitem{Mar.~2019 -- Feb.~2024}{\textbf{Bachelor of Science in Electronics and Communications Engineering}\newline
  Kwangwoon University, Seoul, Republic of Korea \newline
  GPA: 3.41 / 4.5 (88.1\%).}

%==============================================================
\section{Personal skills and competences}

\ecvmothertongue{Korean}
\ecvlanguageheader{(*)}
\ecvlanguage{English}{\ecvBTwo}{\ecvCOne}{\ecvBTwo}{\ecvBTwo}{\ecvBTwo}
\ecvlanguagefooter{(*)}

\ecvitem{Technical skills}{\textbf{Languages:} Python, C/C++, MATLAB, Bash.\newline
  \textbf{Frameworks:} PyTorch, TensorFlow, Transformers, LangChain, NumPy, Pandas, scikit-learn.\newline
  \textbf{Tools:} Linux, Docker, Git, CUDA, VS~Code.\newline
  \textbf{Domains:} Agentic AI, multi-agent LLM systems, GNNs, time-series anomaly detection, biomedical signals.}

\ecvitem{Social skills}{Cross-cultural collaboration across Korean, Canadian, and
  US research environments. Former President of the Kwangwoon International
  Student Association and Class Representative for the Department of Electronics
  and Communications Engineering.}

\ecvitem{Organisational skills}{Director of Filming and Editing at Kwangwoon
  Broadcasting Center (KWBC). Executive Member of the Amateur Radio Club ---
  organised radio workshops and technical exhibitions.}

%==============================================================
\section{Honours and awards}

\ecvitem{Aug.~2022}{\textbf{Achievement Award}, Qualcomm Institute AI Development Project --- UC San Diego, USA.}
\ecvitem{Dec.~2021}{\textbf{Gold Award (Ministerial Award)}, 2021 Smart Maritime Logistics Project --- Minister of Oceans and Fisheries, Republic of Korea.}
\ecvitem{Nov.~2025}{\textbf{Outstanding Student Paper Award}, Conference of the Institute of Electronics and Information Engineers, Republic of Korea.}
\ecvitem{Nov.~2024}{\textbf{Best Poster Award (Silver)}, IBEC 2024.}
\ecvitem{Nov.~2023}{\textbf{Outstanding Paper Award}, KOSOMBE Autumn Conference, Republic of Korea.}
\ecvitem{Dec.~2025}{\textbf{Silver Award}, 23rd Embedded Software Competition (KIISE), Republic of Korea.}

%==============================================================
\section{Publications}

\ecvitem{2026}{R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, J.~Lee$^{\dagger}$, N.~Verma,
  ``CascadeDebate: Multi-Agent Deliberation for Cost-Aware LLM Cascades,''
  \emph{ACL 2026 --- Industry Track (Poster)}. $^{\dagger}$Equal contribution.}

\ecvitem{2025}{J.~Lee$^{\dagger}$, R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, H.~Singh, N.~Verma,
  ``GEMMAS: Graph-based Evaluation Metrics for Multi-Agent Systems,''
  \emph{EMNLP 2025 --- Industry Track (Oral)}. $^{\dagger}$Equal contribution.}

\ecvitem{2025}{\textbf{D.~Kwon} et al., ``Graph-Enhanced Bidirectional GRU for Anomaly
  Detection in Power Generation Environments,'' under review at
  \emph{Data Mining and Knowledge Discovery} (Springer Nature).}

\ecvitem{2024}{\textbf{D.~Kwon} et al., ``Hybrid GAT + Transformer for implantable-device
  anomaly detection,'' \emph{IBEC 2024}. \textbf{Best Poster Award --- Silver.}}

%==============================================================
\section{Patents}

\ecvitem{Apr.~2026}{\textbf{KR 10-2961984} --- Method for Implantable Medical Device to Detect Anomaly in Real Time.}
\ecvitem{Aug.~2025}{\textbf{KR 10-2848814} --- GPT API-Based Network Anomaly Detection.}

\end{europecv}
\end{document}
