%-------------------------
% Upstream Jake Gutierrez Resume Template
% Source: https://github.com/jakegut/resume (MIT)
% GENERATED FROM data/cv.yaml — edit yaml + run scripts/sync.py, not this file.
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{iftex}
\ifPDFTeX
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Dongwook Kwon} \\ \vspace{1pt}
    \small +82 10-6612-9246 $|$
    \href{mailto:dwkwon@suresofttech.com}{\underline{dwkwon@suresofttech.com}} $|$
    \href{https://dongwooky.github.io}{\underline{dongwooky.github.io}} $|$
    \href{https://github.com/dongwooky}{\underline{github.com/dongwooky}} $|$
    \href{https://linkedin.com/in/dongwooky}{\underline{linkedin.com/in/dongwooky}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kwangwoon University}{Seoul, Korea}
      {M.S.\ in Computer Engineering, GPA 4.33 / 4.5 (98.1\%)}{Mar.\ 2024 -- Feb.\ 2026}
    \resumeSubheading
      {University of Toronto}{Toronto, ON, Canada}
      {Graduate Research Program, GPA 3.68 / 4.0}{Jan.\ 2025 -- Jul.\ 2025}
    \resumeSubheading
      {Kwangwoon University}{Seoul, Korea}
      {B.S.\ in Electronics and Communications Engineering, GPA 3.41 / 4.5 (88.1\%)}{Mar.\ 2019 -- Feb.\ 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Engineer, Intelligent Agent Technology Team}{Dec.\ 2025 -- Present}
      {Suresoft Technologies}{Seongnam, Korea}
      \resumeItemListStart
        \resumeItem{Developing an AI validation system utilizing AI agent--based architectures for enterprise model verification.}
        \resumeItem{Designing autonomous and collaborative AI agents that verify and evaluate machine-learning models at scale.}
        \resumeItem{Engineered and delivered a critical agent-based codebase for a mission-critical vehicle control data project for Hyundai Motor Company.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Assistant}{Aug.\ 2021 -- Dec.\ 2025}
      {Bio-Computing \& ML Lab, Kwangwoon University}{Seoul, Korea}
      \resumeItemListStart
        \resumeItem{Researched deep-learning algorithms for anomaly detection in complex time-series data, focusing on critical cyber-physical systems including nuclear power generation environments.}
        \resumeItem{Co-developed an Active Kill-Switch and Biomarker-Based Defense System for life-threatening IoT medical devices.}
      \resumeItemListEnd

    \resumeSubheading
      {Visiting Researcher}{Jan.\ 2025 -- Jul.\ 2025}
      {LG Electronics Canada}{Toronto, ON, Canada}
      \resumeItemListStart
        \resumeItem{Built an LLM-driven assessment framework for evaluating performance of agentic AI systems.}
        \resumeItem{Work fed directly into peer-reviewed publications at EMNLP 2025 and ACL 2026.}
      \resumeItemListEnd

    \resumeSubheading
      {AI Development Project Participant, Summer Program}{Jul.\ 2022 -- Aug.\ 2022}
      {Qualcomm Institute, UC San Diego}{San Diego, CA, USA}
      \resumeItemListStart
        \resumeItem{Built a personality-based drug-addiction prediction system using machine-learning models.}
        \resumeItem{Recognized with the program's Achievement Award.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Agentic AI Evaluation Framework} $|$ \emph{Python, LLMs, multi-agent systems}}{Jan. 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed an evaluation framework for agentic AI systems using LLMs to assess performance.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AI Intrusion Detection for APR1400} $|$ \emph{PyTorch, anomaly detection}}{Jul 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Developed an AI defense system to protect nuclear power plants from cyber attacks.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Quadruped Robot with Vision SLAM} $|$ \emph{ROS, depth camera, SLAM}}{Apr 2022 -- Nov. 2022}
          \resumeItemListStart
            \resumeItem{Developed an autonomous quadruped robot using a navigation algorithm with SLAM and a depth camera.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Smart Logistics System Using Computer Vision} $|$ \emph{OpenCV, container tracking}}{Apr 2021 -- Nov. 2021}
          \resumeItemListStart
            \resumeItem{Developed a logistics detection system incorporating location tracking and stack-layer identification for containers. --- Ministerial Gold Award.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PUBLICATIONS \& PATENTS-----------
\section{Publications \& Patents}
  \resumeSubHeadingListStart
    \item\small{
      R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, J.~Lee$^{\dagger}$, and N.~Verma, ``CascadeDebate: Multi-Agent Deliberation for Cost-Aware LLM Cascades.'' \textit{ACL 2026 --- Industry Track (Poster)}. $^{\dagger}$Equal contribution.    }
    \item\small{
      J.~Lee$^{\dagger}$, R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, H.~Singh, and N.~Verma, ``GEMMAS: Graph-based Evaluation Metrics for Multi Agent Systems.'' \textit{EMNLP 2025 --- Industry Track (Oral)}. $^{\dagger}$Equal contribution.    }
    \item\small{
      \textbf{D.~Kwon}, M.~Kim, Y.~Kang, J.~Lee, and C.~Park, ``Hybrid GAT + Transformer for implantable-device anomaly detection.'' \textit{IBEC 2024}. \textbf{Best Poster Award --- Silver.}    }
    \item\small{
      \textbf{D.~Kwon}, Y.~Kang, and C.~Park, ``Enhancing medical device security with GNN-GRU anomaly detection model.'' \textit{KOSOMBE 2023}. \textbf{Outstanding Paper Award.}    }
    \item\small{
      \textbf{D.~Kwon}, Y.~Kang, J.~Lee, Y.~Nam, J.~Won, K.~K.~Kim, D.~D.~Kim, and C.~Park, ``Graph-Enhanced Bidirectional GRU for Anomaly Detection in Power Generation Environments.'' Under review at \textit{Data Mining and Knowledge Discovery (Springer Nature)}, 2025.
    }
    \item\small{
      Patent \textbf{KR 10-2961984} --- Real-time anomaly detection for implantable medical devices (Apr 2026).
    }
    \item\small{
      Patent \textbf{KR 10-2848814} --- GPT API-Based Network Anomaly Detection (Aug 2025).
    }
    \item\small{
      Patent \textbf{KR 10-2025-0160217} (Pending) --- System for Anomaly Detection Using a Collaborative Multi-AI Determination Module Based on LLM (Oct 2025).
    }
    \item\small{
      Patent \textbf{KR 10-2024-0110559} (Pending) --- Categorical Data of Networks Based Network Anomaly Detection Apparatus and Method Thereof (Aug 2024).
    }
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, MATLAB, Bash} \\
     \textbf{Frameworks}{: PyTorch, TensorFlow, Transformers, LangChain, NumPy, Pandas, scikit-learn} \\
     \textbf{Developer Tools}{: Linux, Docker, Git, CUDA, VS Code} \\
     \textbf{Domains}{: Agentic AI, multi-agent LLM systems, GNNs, time-series anomaly detection, biomedical signals}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
