%!TEX TS-program = xelatex
% Upstream Friggeri CV (Nadorrano fork, MIT) based on Adrien Friggeri's original
% Source: https://github.com/Nadorrano/cv-friggeri-x
% GENERATED FROM data/cv.yaml — edit yaml + run scripts/sync.py, not this file.

\documentclass[]{cv-friggeri-x}

\usepackage{marvosym}

\begin{document}

\header{dongwook}{kwon}{ai engineer \textbullet\ agentic ai systems}

\begin{aside}
\section{contact}
\href{mailto:dwkwon@suresofttech.com}{dwkwon@suresofttech.com}
~
+82 10-6612-9246
~
Seongnam-si, Republic of Korea
~
\href{https://dongwooky.github.io}{dongwooky.github.io}
\href{https://github.com/dongwooky}{github / dongwooky}
\href{https://linkedin.com/in/dongwooky}{in / dongwooky}
\section{languages}
korean (native)
english (fluent)
\section{skills}
{\color{red}$\bullet$} Python, C/C++
{\color{red}$\bullet$} PyTorch, Transformers
{\color{red}$\bullet$} LangChain, LLMs
{\color{red}$\bullet$} Linux, Docker, CUDA
{\color{red}$\bullet$} GNNs, time-series
{\color{red}$\bullet$} biomedical signals
\section{interests}
multi-agent LLMs
anomaly detection
nuclear cybersecurity
amateur radio
\end{aside}

\section{education}

\begin{entrylist}
\entry
  {2024--2026}
  {M.S.\ {\normalfont in Computer Engineering}}
  {Kwangwoon University, Seoul}
  {GPA 4.33 / 4.5 (98.1\%). Bio-Computing \& Machine Learning Laboratory.}

\entry
  {2025}
  {Graduate Research Program}
  {University of Toronto}
  {GPA 3.68 / 4.0. Mechanical and Industrial Engineering.}

\entry
  {2019--2024}
  {B.S.\ {\normalfont in Electronics and Communications Engineering}}
  {Kwangwoon University, Seoul}
  {GPA 3.41 / 4.5 (88.1\%).}

\end{entrylist}

\section{experience}

\begin{entrylist}
\entry
  {2025--Now}
  {SURESOFT TECHNOLOGIES}
  {Seongnam, Korea}
  {\emph{AI Engineer, Intelligent Agent Technology Team.} Developing AI validation system using agentic AI architectures for enterprise model verification. Designing autonomous and collaborative agents for systematic AI verification. }

\entry
  {2021--2025}
  {BIO-COMPUTING \& ML LAB, KWANGWOON U.}
  {Seoul, Korea}
  {\emph{Research Assistant.} Deep-learning anomaly detection in time-series (ECG, cyber-physical systems). EMNLP 2025 (Oral), ACL 2026; two granted KR patents. }

\entry
  {2025}
  {LG ELECTRONICS CANADA}
  {Toronto, ON, Canada}
  {\emph{Visiting Researcher.} Built LLM-driven assessment framework for evaluating agentic AI systems. }

\entry
  {2022}
  {QUALCOMM INSTITUTE, UC SAN DIEGO}
  {San Diego, CA, USA}
  {\emph{AI Development Project Participant, Summer Program.} Personality-based drug-addiction prediction. Achievement Award. }

\end{entrylist}

\section{publications}

\begin{entrylist}
\entry
  {2026}
  {CascadeDebate: Multi-Agent Deliberation for Cost-Aware LLM Cascades}
  {ACL 2026 --- Industry Track (Poster)}
  {R. Chang$^{\dagger}$, \textbf{D. Kwon}$^{\dagger}$, J. Lee$^{\dagger}$, and N. Verma. $^{\dagger}$Equal contribution.}

\entry
  {2025}
  {GEMMAS: Graph-based Evaluation Metrics for Multi Agent Systems}
  {EMNLP 2025 --- Industry Track (Oral)}
  {J. Lee$^{\dagger}$, R. Chang$^{\dagger}$, \textbf{D. Kwon}$^{\dagger}$, H. Singh, and N. Verma. $^{\dagger}$Equal contribution.}

\entry
  {2024}
  {Hybrid GAT + Transformer for implantable-device anomaly detection}
  {IBEC 2024 --- Best Poster Silver}
  {\textbf{D. Kwon}, M. Kim, Y. Kang, J. Lee, and C. Park.}

\entry
  {2023}
  {Enhancing medical device security with GNN-GRU anomaly detection model}
  {KOSOMBE 2023 --- Outstanding Paper Award}
  {\textbf{D. Kwon}, Y. Kang, and C. Park.}

\entry
  {2025}
  {Graph-Enhanced Bidirectional GRU for Anomaly Detection in Power Generation}
  {Data Mining \& Knowledge Discovery (under review)}
  {\textbf{D. Kwon} et al.}

\end{entrylist}

\section{awards}

\begin{entrylist}
\entry
  {2022}
  {Achievement Award}
  {Qualcomm Institute AI Development Project --- UC San Diego}
  {Honored for project work during the summer program.}

\entry
  {2021}
  {Gold Award (Ministerial)}
  {2021 Smart Maritime Logistics Project --- Minister of Oceans and Fisheries}
  {Top award for project on container detection and stack-layer identification.}

\entry
  {2025}
  {Silver Award}
  {23rd Embedded Software Competition (KIISE)}
  {Recognition at one of Korea's flagship embedded-software competitions.}

\end{entrylist}

\section{patents}

\begin{entrylist}
\entry
  {2026}
  {Method for Implantable Medical Device to Detect Anomaly in Real Time}
  {KR 10-2961984}
  {Issued patent, Republic of Korea. April 30, 2026.}

\entry
  {2025}
  {GPT API-Based Network Anomaly Detection}
  {KR 10-2848814}
  {Issued patent, Republic of Korea. August 18, 2025.}

\end{entrylist}

\end{document}
