%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Upstream Awesome-CV (posquit0) — class file copied locally unmodified.
% Source: https://github.com/posquit0/Awesome-CV (CC BY-SA 4.0)
% GENERATED FROM data/cv.yaml — edit yaml + run scripts/sync.py, not this file.

\documentclass[11pt, letterpaper]{awesome-cv}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

\colorlet{awesome}{awesome-red}
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\name{Dongwook}{Kwon}
\position{AI Engineer {\enskip\cdotp\enskip} Agentic AI Systems}
\address{11F, 37, Geumto-ro 80beon-gil, Sujeong-gu, Seongnam-si, Gyeonggi-do, 13453, South Korea}
\mobile{(+82) 10-6612-9246}
\email{dwkwon@suresofttech.com}
\homepage{dongwooky.github.io}
\github{dongwooky}
\linkedin{dongwooky}

\begin{document}

\makecvheader[C]
\makecvfooter
  {\today}
  {Dongwook Kwon~~~·~~~Curriculum Vitae}
  {\thepage}

%-------------------------------------------------------------------------------
\cvsection{Experience}
\begin{cventries}
  \cventry
    {AI Engineer, Intelligent Agent Technology Team}
    {Suresoft Technologies}
    {Seongnam-si, Korea}
    {Dec.\ 2025 - Present}
    {
      \begin{cvitems}
        \item {Developing an AI validation system utilizing AI agent-based architectures for enterprise model verification.}
        \item {Designing autonomous and collaborative AI agents that verify and evaluate machine-learning models at scale.}
        \item {Building agentic AI systems to enable systematic, scalable, and reliable AI verification processes.}
      \end{cvitems}
    }
  \cventry
    {Research Assistant}
    {Bio-Computing and Machine Learning Laboratory, Kwangwoon University}
    {Seoul, Korea}
    {Aug.\ 2021 - Dec.\ 2025}
    {
      \begin{cvitems}
        \item {Researched deep-learning algorithms for anomaly detection in time-series data (ECG, cyber-physical systems).}
        \item {Co-developed an Active Kill-Switch and Biomarker-Based Defense System for life-threatening IoT medical devices.}
        \item {Published in EMNLP 2025 (Oral) and ACL 2026; co-author on two granted Republic of Korea patents.}
      \end{cvitems}
    }
  \cventry
    {Visiting Researcher}
    {LG Electronics Canada (with University of Toronto)}
    {Toronto, ON, Canada}
    {Jan.\ 2025 - Jul.\ 2025}
    {
      \begin{cvitems}
        \item {Built an LLM-driven assessment framework for evaluating performance of agentic AI systems.}
        \item {Work fed directly into peer-reviewed publications at EMNLP 2025 and ACL 2026.}
      \end{cvitems}
    }
  \cventry
    {AI Development Project Participant, Summer Program}
    {Qualcomm Institute, University of California San Diego}
    {San Diego, CA, USA}
    {Jul.\ 2022 - Aug.\ 2022}
    {
      \begin{cvitems}
        \item {Built a personality-based drug-addiction prediction system using machine-learning models.}
        \item {Recognized with the program's Achievement Award.}
      \end{cvitems}
    }
\end{cventries}

%-------------------------------------------------------------------------------
\cvsection{Education}
\begin{cventries}
  \cventry
    {Master of Science in Computer Engineering}
    {Kwangwoon University}
    {Seoul, Korea}
    {Mar.\ 2024 - Feb.\ 2026}
    {
      \begin{cvitems}
        \item {GPA: 4.33/4.5 (98.1\%)}
      \end{cvitems}
    }
  \cventry
    {Graduate Research Program in Mechanical and Industrial Engineering}
    {University of Toronto}
    {Toronto, ON, Canada}
    {Jan.\ 2025 - Jul.\ 2025}
    {
      \begin{cvitems}
        \item {GPA: 3.68/4.0}
      \end{cvitems}
    }
  \cventry
    {Bachelor of Science in Electronics and Communications Engineering}
    {Kwangwoon University}
    {Seoul, Korea}
    {Mar.\ 2019 - Feb.\ 2024}
    {
      \begin{cvitems}
        \item {GPA: 3.41/4.5 (88.1\%)}
      \end{cvitems}
    }
\end{cventries}

%-------------------------------------------------------------------------------
\cvsection{Honors \& Awards}

\cvsubsection{Major Awards}
\begin{cvhonors}
  \cvhonor{Achievement Award}{Qualcomm Institute AI Development Project --- UC San Diego}{United States}{Aug.\ 2022}
  \cvhonor{Gold Award (Ministerial Award)}{2021 Smart Maritime Logistics Project --- Minister of Oceans and Fisheries}{South Korea}{Dec.\ 2021}
\end{cvhonors}

\cvsubsection{Academic Recognition}
\begin{cvhonors}
  \cvhonor{Outstanding Student Paper Award}{Conference of the Institute of Electronics and Information Engineers}{South Korea}{Nov.\ 2025}
  \cvhonor{Best Poster Award (Silver)}{10th International Biomedical Engineering Conference (IBEC 2024)}{South Korea}{Nov.\ 2024}
  \cvhonor{Outstanding Paper Award}{Conference of the Korean Society of Medical and Biological Engineering}{South Korea}{Nov.\ 2023}
\end{cvhonors}

\cvsubsection{Competitions}
\begin{cvhonors}
  \cvhonor{Silver Award}{23rd Embedded Software Competition (KIISE)}{South Korea}{Dec.\ 2025}
  \cvhonor{Bronze Award}{Hanium ICT Mentoring Competition --- FKII}{South Korea}{Dec.\ 2022}
  \cvhonor{Excellence Award}{18th Kwangwoon ICT Exhibition (KWIX) --- Kwangwoon University}{South Korea}{Sep.\ 2022}
  \cvhonor{Grand Prize}{MY (Multi-Y) Capstone Design Competition --- Kwangwoon University}{South Korea}{Oct.\ 2021}
\end{cvhonors}

%-------------------------------------------------------------------------------
\cvsection{Funded Research Projects}
\begin{cventries}
  \cventry{Agentic AI Evaluation Framework}{LG Electronics Canada}{Toronto, ON, Canada}{Jan.\ 2025 - Present}
  {\begin{cvitems}\item {Developed an evaluation framework for agentic AI systems using LLMs to assess performance.}\end{cvitems}}

  \cventry{AI-based Intrusion Detection and Attack Packet Crafting Technologies for APR1400}{Sejong University}{Seoul, Korea}{Jul.\ 2022 - Present}
  {\begin{cvitems}\item {Developed an AI defense system to protect nuclear power plants from cyber attacks.}\end{cvitems}}

  \cventry{Quadruped Robot Using Vision SLAM with a Depth Camera}{Ministry of Science and ICT}{Seoul, Korea}{Apr.\ 2022 - Nov.\ 2022}
  {\begin{cvitems}\item {Developed an autonomous quadruped robot using a navigation algorithm with SLAM and a depth camera.}\end{cvitems}}

  \cventry{Personality-Based Drug Addiction Prediction System}{Qualcomm Institute, University of California San Diego}{San Diego, CA, USA}{Jul.\ 2022 - Aug.\ 2022}
  {\begin{cvitems}\item {Developed a personality-based drug addiction prediction system using a machine learning model.}\end{cvitems}}

  \cventry{Development of Active Kill-Switch and Biomarker-Based Defense System for Life-Threatening IoT Medical Devices}{Kookmin University}{Seoul, Korea}{Sep.\ 2021 - Dec.\ 2022}
  {\begin{cvitems}\item {Developed a security system for heart implant devices using an anomaly detection algorithm.}\end{cvitems}}

  \cventry{Development of a Smart Logistics System Using Computer Vision}{Ministry of Oceans and Fisheries}{Seoul, Korea}{Apr.\ 2021 - Nov.\ 2021}
  {\begin{cvitems}\item {Developed a logistics detection system incorporating location tracking and stack-layer identification for containers.}\end{cvitems}}

  \cventry{Smart Kitchen IoT System Utilizing Computer Vision and Deep Learning}{Kwangwoon University}{Seoul, Korea}{May 2021 - Oct.\ 2021}
  {\begin{cvitems}\item {Developed a cloud IoT platform featuring a system for classifying groceries in the fridge and an OCR receipt program.}\end{cvitems}}

\end{cventries}

%-------------------------------------------------------------------------------
\cvsection{Publications}

\cvsubsection{Journal Articles}
\begin{cvparagraph}
Y.~Nam, J.~Lee, H.~Lee, \textbf{D.~Kwon}, M.~Yeo, S.~Kim, R.~Sohn, and C.~Park, ``Designing a remote photoplethysmography-based heart rate estimation algorithm during a treadmill exercise,'' \emph{Electronics}, vol.~14, no.~5, p.~890, 2025.

\textbf{D.~Kwon}, Y.~Kang, J.~Lee, Y.~Nam, J.~Won, K.~K.~Kim, D.~D.~Kim, and C.~Park, ``Graph-Enhanced Bidirectional GRU for Anomaly Detection in Power Generation Environments,'' under review at \emph{Data Mining and Knowledge Discovery (Springer Nature)}, 2025.

\end{cvparagraph}

\cvsubsection{Conference Papers}
\begin{cvparagraph}
R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, J.~Lee$^{\dagger}$, and N.~Verma, ``CascadeDebate: Multi-Agent Deliberation for Cost-Aware LLM Cascades,'' in \emph{Proc.~64th Annu.\ Meeting Assoc.\ Comput.\ Linguistics (ACL) --- Industry Track (Poster)}, 2026. $^{\dagger}$Equal contribution.
J.~Lee$^{\dagger}$, R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, H.~Singh, and N.~Verma, ``GEMMAS: Graph-based Evaluation Metrics for Multi Agent Systems,'' in \emph{Proceedings of the EMNLP 2025 Industry Track (Oral)}, 2025. $^{\dagger}$Equal contribution.
\textbf{D.~Kwon}, M.~Kim, Y.~Kang, J.~Lee, and C.~Park, ``Hybrid neural network model for anomaly detection in implantable devices using graph attention networks and transformers,'' in \emph{Proc.\ 10th Int.\ Biomed.\ Eng.\ Conf.\ (IBEC)}, 2024. \textbf{Best Poster Award --- Silver.}
\textbf{D.~Kwon}, Y.~Kang, and C.~Park, ``Enhancing medical device security with GNN-GRU anomaly detection model,'' in \emph{Proc.\ 62nd KOSOMBE Autumn Conf.}, pp.~204--205, 2023. \textbf{Outstanding Paper Award.}
\end{cvparagraph}

%-------------------------------------------------------------------------------
\cvsection{Patents}
\begin{cvhonors}
  \cvhonor{Method for Implantable Medical Device to Detect Anomaly in Real Time}{KR 10-2961984}{Republic of Korea}{Apr 2026}
  \cvhonor{GPT API-Based Network Anomaly Detection}{KR 10-2848814}{Republic of Korea}{Aug 2025}
\end{cvhonors}

%-------------------------------------------------------------------------------
\cvsection{Leadership Experience}
\begin{cventries}
  \cventry
    {President}
    {Kwangwoon International Student Association}
    {}
    {}
    {
      \begin{cvitems}
        \item {Lead intercultural programs and student engagement initiatives.}
      \end{cvitems}
    }
  \cventry
    {Director of Filming and Editing}
    {Kwangwoon Broadcasting Center (KWBC)}
    {}
    {}
    {
      \begin{cvitems}
        \item {Oversaw media production and content delivery.}
      \end{cvitems}
    }
  \cventry
    {Class Representative}
    {Dept. of Electronics and Communications Engineering}
    {}
    {}
    {
      \begin{cvitems}
        \item {Represented student interests in academic affairs.}
      \end{cvitems}
    }
  \cventry
    {Executive Member}
    {Amateur Radio Club}
    {}
    {}
    {
      \begin{cvitems}
        \item {Organized radio workshops and technical exhibitions.}
      \end{cvitems}
    }
\end{cventries}

\end{document}
