% Upstream ModernCV by Xavier Danaux (CTAN)
% Source: https://ctan.org/pkg/moderncv (LPPL)
% Class shipped with TeX Live — no local .cls copy needed.

\documentclass[11pt,letterpaper,sans]{moderncv}

% Styles: classic, casual, banking, oldstyle, fancy
\moderncvstyle{banking}
% Colors: blue, orange, green, red, purple, grey, black
\moderncvcolor{blue}

\usepackage[scale=0.82,top=1.0in,bottom=1.0in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*,itemsep=0.2em,topsep=0.1em}

% Widen the date column (left margin) to fit longer date ranges
\setlength{\hintscolumnwidth}{1.6in}
\AtBeginDocument{\recomputelengths}

% --- Personal data ---
\name{Dongwook}{Kwon}
\title{AI Engineer \textbullet\ Agentic AI Systems}
\address{Room 701, Saebit Hall, 20 Gwangun-ro, Nowon-gu}{Seoul 01897, Republic of Korea}{}
\phone[mobile]{+82~10-6612-9246}
\email{tomiyadragon@gmail.com}
\homepage{dongwooky.github.io}
\social[github]{dongwooky}
\social[linkedin]{dongwooky}

\begin{document}
\makecvtitle

%---------------- EXPERIENCE ----------------
\section{Experience}

\cventry{Dec.\ 2025 -- Present}{AI Engineer, Intelligent Agent Technology Team}{Suresoft Technologies}{Seongnam, Korea}{}{%
  \begin{itemize}
    \item Developing an AI validation system utilizing AI agent--based architectures.
    \item Designing and implementing systems to verify and evaluate AI models through autonomous and collaborative AI agents.
    \item Building agentic AI systems to enable systematic, scalable, and reliable AI verification processes.
  \end{itemize}}

\cventry{Aug.\ 2021 -- Dec.\ 2025}{Research Assistant}{Bio-Computing and Machine Learning Laboratory, Kwangwoon University}{Seoul, Korea}{}{%
  \begin{itemize}
    \item Conducted research on deep learning algorithms for anomaly detection in time-series data, including ECG and Cyber-Physical Systems.
    \item Participated in the development of an Active Kill-Switch and Biomarker-Based Defense System for life-threatening IoT medical devices.
  \end{itemize}}

\cventry{Jan.\ 2025 -- Jul.\ 2025}{Visiting Researcher}{LG Electronics Canada (with University of Toronto)}{Toronto, ON, Canada}{}{%
  \begin{itemize}
    \item Participating in the development of an assessment framework for agentic AI systems utilizing LLMs to evaluate performance.
  \end{itemize}}

\cventry{Jul.\ 2022 -- Aug.\ 2022}{AI Development Project, Summer Program}{Qualcomm Institute, UC San Diego}{San Diego, CA, USA}{}{%
  \begin{itemize}
    \item Participated in the Personality-Based Drug Addiction Prediction System project.
    \item Attended seminars on deep learning and machine learning algorithms.
  \end{itemize}}

%---------------- EDUCATION ----------------
\section{Education}

\cventry{Mar.\ 2024 -- Feb.\ 2026}{M.S.\ in Computer Engineering}{Kwangwoon University}{Seoul, Korea}{\textit{GPA: 4.33/4.5 (98.1\%)}}{}

\cventry{Jan.\ 2025 -- Jul.\ 2025}{Graduate Research Program}{University of Toronto}{Toronto, ON, Canada}{\textit{Mechanical and Industrial Engineering; GPA: 3.68/4.0}}{}

\cventry{Mar.\ 2019 -- Feb.\ 2024}{B.S.\ in Electronics and Communications Engineering}{Kwangwoon University}{Seoul, Korea}{\textit{GPA: 3.41/4.5 (88.1\%)}}{}

%---------------- HONORS & AWARDS ----------------
\section{Honors \& Awards}

\subsection{Major Awards}
\cvitem{Aug.\ 2022}{\textbf{Achievement Award}, Qualcomm Institute AI Development Project --- UC San Diego \hfill \textit{United States}}
\cvitem{Dec.\ 2021}{\textbf{Gold Award (Ministerial Award)}, 2021 Smart Maritime Logistics Project -- Minister of Oceans and Fisheries \hfill \textit{South Korea}}

\subsection{Academic Recognition}
\cvitem{Nov.\ 2025}{\textbf{Outstanding Student Paper Award}, Conference of the Institute of Electronics and Information Engineers \hfill \textit{South Korea}}
\cvitem{Nov.\ 2024}{\textbf{Best Poster Award (Silver)}, 10th International Biomedical Engineering Conference (IBEC 2024) \hfill \textit{South Korea}}
\cvitem{Nov.\ 2023}{\textbf{Outstanding Paper Award}, Conference of the Korean Society of Medical and Biological Engineering \hfill \textit{South Korea}}

\subsection{Competitions}
\cvitem{Dec.\ 2025}{\textbf{Silver Award}, 23rd Embedded Software Competition (KIISE) \hfill \textit{South Korea}}
\cvitem{Dec.\ 2022}{\textbf{Bronze Award}, Hanium ICT Mentoring Competition -- FKII \hfill \textit{South Korea}}
\cvitem{Sep.\ 2022}{\textbf{Excellence Award}, 18th Kwangwoon ICT Exhibition (KWIX) --- Kwangwoon University \hfill \textit{South Korea}}
\cvitem{Oct.\ 2021}{\textbf{Grand Prize}, MY (Multi-Y) Capstone Design Competition --- Kwangwoon University \hfill \textit{South Korea}}

%---------------- PROJECTS ----------------
\section{Funded Research Projects}

\cventry{Jan.\ 2025 -- Present}{Agentic AI Evaluation Framework}{LG Electronics Canada}{Toronto, ON, Canada}{}{Developed an evaluation framework for agentic AI systems using LLMs to assess performance.}

\cventry{Jul.\ 2022 -- Present}{AI-based Intrusion Detection for APR1400}{Sejong University}{Seoul, Korea}{}{Developed an AI defense system to protect nuclear power plants from cyber attacks.}

\cventry{Apr.\ 2022 -- Nov.\ 2022}{Quadruped Robot Using Vision SLAM}{Ministry of Science and ICT}{Seoul, Korea}{}{Developed an autonomous quadruped robot using a navigation algorithm with SLAM and a depth camera.}

\cventry{Sep.\ 2021 -- Dec.\ 2022}{Active Kill-Switch and Biomarker-Based Defense for IoT Medical Devices}{Kookmin University}{Seoul, Korea}{}{Developed a security system for heart implant devices using an anomaly detection algorithm.}

\cventry{Apr.\ 2021 -- Nov.\ 2021}{Smart Logistics System Using Computer Vision}{Ministry of Oceans and Fisheries}{Seoul, Korea}{}{Developed a logistics detection system incorporating location tracking and stack-layer identification for containers.}

%---------------- PUBLICATIONS ----------------
\section{Publications}

\subsection{Journal Articles}
\cvitem{2025}{Y.~Nam, J.~Lee, H.~Lee, \textbf{D.~Kwon}, M.~Yeo, S.~Kim, R.~Sohn, and C.~Park, ``Designing a remote photoplethysmography-based heart rate estimation algorithm during a treadmill exercise,'' \emph{Electronics}, vol.~14, no.~5, p.~890, 2025.}
\cvitem{2025}{\textbf{D.~Kwon}, Y.~Kang, J.~Lee, Y.~Nam, J.~Won, K.~K.~Kim, D.~D.~Kim, and C.~Park, ``Graph-Enhanced Bidirectional GRU for Anomaly Detection in Power Generation Environments,'' under review at \emph{Data Mining and Knowledge Discovery} (Springer Nature), 2025.}

\subsection{Conference Papers}
\cvitem{2026}{R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, J.~Lee$^{\dagger}$, and N.~Verma, ``CascadeDebate: Multi-Agent Deliberation for Cost-Aware LLM Cascades,'' in \emph{Proc.~64th Annu.\ Meeting Assoc.\ Comput.\ Linguistics (ACL) -- Industry Track (Poster)}, 2026.\ \ $^{\dagger}$Equal contribution.}
\cvitem{2025}{J.~Lee$^{\dagger}$, R.~Chang$^{\dagger}$, \textbf{D.~Kwon}$^{\dagger}$, H.~Singh, and N.~Verma, ``GEMMAS: Graph-based Evaluation Metrics for Multi Agent Systems,'' in \emph{Proceedings of the EMNLP 2025 Industry Track (Oral)}, 2025.\ \ $^{\dagger}$Equal contribution.}
\cvitem{2024}{\textbf{D.~Kwon}, M.~Kim, Y.~Kang, J.~Lee, and C.~Park, ``Hybrid neural network model for anomaly detection in implantable devices using graph attention networks and transformers,'' in \emph{Proc.\ 10th Int.\ Biomed.\ Eng.\ Conf.\ (IBEC)}, 2024.\ \textbf{Best Poster Award -- Silver.}}
\cvitem{2023}{\textbf{D.~Kwon}, Y.~Kang, and C.~Park, ``Enhancing medical device security with GNN-GRU anomaly detection model,'' in \emph{Proc.\ 62nd KOSOMBE Autumn Conf.}, pp.~204--205, 2023.\ \textbf{Outstanding Paper Award.}}

%---------------- PATENTS ----------------
\section{Patents}
\cvitem{Apr.\ 2026}{\textbf{Issued Patent}, ``Method for Implantable Medical Device to Detect Anomaly in Real Time,'' KR 10-2961984.}
\cvitem{Aug.\ 2025}{\textbf{Issued Patent}, ``GPT API-Based Network Anomaly Detection,'' KR 10-2848814.}

%---------------- LEADERSHIP ----------------
\section{Leadership Experience}
\cvitem{}{\textbf{President}, Kwangwoon International Student Association --- Lead intercultural programs and student engagement initiatives.}
\cvitem{}{\textbf{Director of Filming and Editing}, Kwangwoon Broadcasting Center (KWBC) --- Oversaw media production and content delivery.}
\cvitem{}{\textbf{Class Representative}, Dept.\ of Electronics and Communications Engineering --- Represented student interests in academic affairs.}
\cvitem{}{\textbf{Executive Member}, Amateur Radio Club --- Organized radio workshops and technical exhibitions.}

\end{document}
